\begin{thebibliography}{11}
%capitulo 1
%Trabajos RELACIONADOS
\bibitem{akamai:2016}
Akamai (2016).''Q1 2016 State of the Internet''. Available: \url{https://www.akamai.com/uk/en/about/news/press/2016-press/akamai-releases-first-quarter-2016-state-of-the-internet-security-report.jsp}

\bibitem{sans}
SANS Institute (2014). ''DDoS Attacks Advancing and Enduring: A SANS Survey''. Available: \url{https://www.sans.org/reading-room/whitepapers/analyst/ddos-attacks-advancing-enduring-survey-34700}

\bibitem{peng:2007}
T. Peng, C. Leckie, K. Ramamohanarao. ''Survey of network-based defense mechanisms countering the DoS and DDoS problems'', \textit{ACM Computing Surveys}, Vol. 39 (1), no. 3, pp. 1-42, 2007.

\bibitem{sniper:2014}
R. Jansen, F. Tschorsch, A. Johnson, B. Scheuermann, ''The Sniper Attack: Anonymously Deanonymizing and Disabling the Tor Network'', \textit{in Proc. of the 18th Symposium on Network and Distributed System Security (NDSS)}, San Diego, Ca, US, August 2014.

\bibitem{douligeris:2004}
C. Douligeris, A. Mitrokotsa, ''DDoS attacks and defense mechanisms: classification and state-of-the-art'', \textit{Computer Networks}, Vol. 44 (5), pp. 643–666, April 2004.

\bibitem{zargar:2013}
S. T. Zargar, J. Joshi, D. Tipper. ''A Survey of Defense Mechanisms Against Distributed Denial of Service (DDoS) Flooding Attacks'', \textit{IEEE Communications Surveys \& Tutorials}, Vol. 15 (4), pp. 2046-2069, March 2013.

\bibitem{voip:2008}
H. Sengar, H. Wang, D. Wijesekera, S. Jajodia. ''Detecting VoIP Floods Using the Hellinger Distance'', \textit{IEEE Transactions on  Parallel and Distributed Systems}, Vol. 19 (6), pp. 794-805, June 2008.

\bibitem{dns:2013}
M. Anagnostopoulos, G. Kambourakis, P. Kopanos, G. Louloudakis, S. Gritzalis. ''DNS amplification attack revisited'', \textit{Computers \& Security}, Vol. 39, part B, pp. 475-485, November 2013.

\bibitem{detection:2014}
W. Zhou, W. Jia, S. Wen, Y. Xiang, W. Zhou. ''Detection and defense of application-layer DDoS attacks in backbone web traffic'', \textit{Future Generation Computer Systems}, vol. 38, pp. 36-46, January 2014.

\bibitem{markov:2013}
S. Shin, S. Lee, H. Kim, S. Kim. ''Advanced probabilistic approach for network intrusion forecasting and detection'', \textit{Expert Systems with Applications}, Vol. 40, no. 1, pp. 315-322, 2013.

\bibitem{genetic:2012}
S.M. Lee, D.S. Kim, J.H. Lee, J.S. Park. ''Detection of DDoS attacks using optimized traffic matrix'', \textit{Computers \& Mathematics with Applications}, Vol. 63, no. 2, pp. 501-510, September 2012.

\bibitem{chaos:2013}
Y. Chen, X. Ma, X. Wu. ''DDoS detection algorithm based on preprocessing network traffic predicted method and chaos theory'', \textit{IEEE Communications Letters}, Vol. 17, no. 5, pp. 1052-1054, May 2013.

\bibitem{wavelets:2012}
C. Callegari, S. Giordano, M. Pagano, T. Pepe. ''Wave-cusum: improving cusum performance in network anomaly detection by means of wavelet analysis'', \textit{Computers \& Security}, Vol. 31, no. 5, pp. 727-7J5, July 2012.

\bibitem{logic:2013}
P.A.R. Kumar, S. Selvakumar. ''Detection of distributed denial of service attacks using an ensemble of adaptive and hybrid neuro-fuzzy systems'', \textit{Computer Communications}, Vol. 36, no. 3, pp. 303-19, February 2013.

\bibitem{entropy1:2015}
I. Ozcelik, R.R. Brooks. ''Deceiving entropy based DoS detection'', \textit{Computers \& Security}, Vol. 48, no. 1, pp. 234-245, February 2015.

\bibitem{entropy2:2015}
M.H. Bhuyan, D. K. Bhattacharyya, J.K. Kalita. ''An empirical evaluation of information metrics for low-rate and high-rate DDoS attack detection'', \textit{Pattern Recognition Letters}, Vol. 51, no. 1, pp. 1-7, January 2015.

\bibitem{traceback:2014}
A.R. Kiremire, M.R. Brust, V.V. Phoha. ''Using network motifs to investigate the influence of network topology on PPM-based IP traceback schemes'', \textit{Computer Networks}, Vol. 72 (1), pp. 14-32, October 2014.

\bibitem{traceback2:2014}
N.M. Alenezi, M.J. Reed. ''Uniform DoS traceback'', \textit{Computers \& Security}, Vol. 45 (1), pp. 17-26, September 2014.

\bibitem{mitigation:2012}
S. Khanna, S.S. Venkatesh, O. Fatemieh, F. Khan, C.A. Gunter. ''Adaptive selective verification: an efficient adaptive countermeasure to thwart DoS attacks'', \textit{IEEE/ACM Transactions on Netwowking}, Vol. 20 (3), pp.  715–728, June 2012.

\bibitem{caida}
The CAIDA UCSD (2015), ''DDoS Attack 2007 Dataset''. Available: \url{http://www.caida.org/data/passive/ddos-20070804\_dataset.xml}

\bibitem{caida2}
The CAIDA UCSD (2015), ''Anonymized Internet Traces 2008''. Available: \url{http://www.caida.org/data/passive/passive\_2008\_dataset.xml}

\bibitem{shannon-entropy}
C.E. Shannon. ''A mathematical theory of communication'', \textit{Bell system technical journal}, Vol. 27, pp.397-423, 1948.

\bibitem{renyi-entropy}
A. Rènyi. ''On measures of entropy and information'', \textit{in Proc. of the 4th Berkeley symposium on mathematical statistics and probability}, Berkeley, CA, US, Vol. 1, 547-561, June 1961.

\bibitem{mafiaboy}
MafiaBoy. \url{https://en.wikipedia.org/wiki/MafiaBoy}

\bibitem{ntp-attack}
PCMag (2014). Available: \url{http://www.pcmag.com/article2/0,2817,2453157,00.asp}

\bibitem{varios-2016}
Radware (2016). Available: \url{https://blog.radware.com/security/2016/01/top-ddos-attacks-2015/}

\bibitem{top-602}
TheHackerNews (2016). Available: \url{http://thehackernews.com/2016/01/biggest-ddos-attack.html}

\bibitem{cloudfare}
Cloudfare (2013). Available: \url{https://blog.cloudflare.com/the-ddos-that-knocked-spamhaus-offline-and-ho/}

\bibitem{charlie}
The Whir (2015). Available: \url{http://www.thewhir.com/web-hosting-news/thousands-french-websites-face-ddos-attacks-since-charlie-hebdo-massacre}

\bibitem{botnet-art}
Rafael A. Rodríguez Gómez, Gabriel Maciá Fernández, Pedro García Teodoro. ''Survey and Taxonomy of Botnet Research through Life-Cycle'', 2013.

\bibitem{botnet-ej}
We Live Security (2015). Available: \url{http://www.welivesecurity.com/2015/02/25/nine-bad-botnets-damage/}

\bibitem{synflood}
Wikipedia. Available: \url{https://en.wikipedia.org/wiki/SYN\_flood}

\bibitem{soa-dos}
Saman Taghavi Zargar, James Joshi, David Tipper. ''A Survey of Defense Mechanisms Against Distributed Denial of Service (DDoS) Flooding Attacks, \textit{IEEE Communications Surveys \& Tutorials}, Vol. 15 No. 4, Fourth Quarter 2013.

\bibitem{ntp-cloudfare}
Cloudfare (2014). ''Understanding and mitigating NTP-based DDoS attacks''. Available: \url{https://blog.cloudflare.com/understanding-and-mitigating-ntp-based-ddos-attacks/}

\bibitem{bhatia}
S. Bhatia, D. Schmidt, G. Mohay, A. Tickle. ''A framework for generating realistic traffic for Distributed Denial of Service attacks and Flash Events'', \textit{Computers \& Security}, Vol. 40, no. 1, pp. 95-107, February 2014.

\end{thebibliography}
